Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-17 Grassmannian_cells.tex
...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians}
\label{QG}

In this section, we aim to establish the existence of cell decompositions for quiver Grassmannians of (truncated) preprojective representations of $K(n)$ and its universal covering quiver.
By a \emph{cell decomposition} of an algebraic variety $X$, we mean a filtration $\varnothing=X_{k+1}\subset X_k\subset \cdots \subset X_2\subset X_1=X$ of $X$ by closed subsets $X_i\subset X$ so that each $X_i\setminus X_{i+1}$ is isomorphic to an affine space.
Alternatively, a cell decomposition of $X$ is a collection of disjoint subsets $U_1,\ldots,U_k\subset X$, each isomorphic to an affine space, such that each $X_i=U_i\sqcup U_{i+1}\sqcup\cdots\sqcup U_k$ is closed in $X$ with $X_1=X$.
We call the subsets $U_i\subset X$ the \emph{affine cells} for this cell decomposition.
Given varieties $X$ and $Y$ each with cell decompositions, we may choose an ordering on products of their affine cells (e.g.\ lexicographic) to get a cell decomposition of $X\times Y$. 
Given a variety $X$ with a cell decomposition, we call a subvariety $U\subset X$ \emph{compatible} with the cell decomposition if $U$ can be written as the union of a subset of the affine cells for $X$.
In this case, $U$ also has a cell decomposition given by taking exactly those affine cells which are contained in $U$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians}
\label{QG}
\noindent 
In this section, we aim to establish the existence of cell decompositions for quiver Grassmannians of (truncated) preprojective representations of $K(n)$ and its universal covering quiver.
By a \emph{cell decomposition} of an algebraic variety $X$, we mean a filtration $\varnothing=X_{k+1}\subset X_k\subset \cdots \subset X_2\subset X_1=X$ of $X$ by closed subsets $X_i\subset X$ so that each $X_i\setminus X_{i+1}$ is isomorphic to an affine space.
Alternatively, a cell decomposition of $X$ is a collection of disjoint subsets $U_1,\ldots,U_k\subset X$, each isomorphic to an affine space, such that each $X_i=U_i\sqcup U_{i+1}\sqcup\cdots\sqcup U_k$ is closed in $X$ with $X_1=X$.
We call the subsets $U_i\subset X$ the \emph{affine cells} for this cell decomposition.
Given varieties $X$ and $Y$ each with cell decompositions, we may choose an ordering on products of their affine cells (e.g.\ lexicographic) to get a cell decomposition of $X\times Y$. 
Given a variety $X$ with a cell decomposition, we call a subvariety $U\subset X$ \emph{compatible} with the cell decomposition if $U$ can be written as the union of a subset of the affine cells for $X$.
In this case, $U$ also has a cell decomposition given by taking exactly those affine cells which are contained in $U$.
